### 2022-11-08 doc/src/AdvPLIC.tex
Update to 1.0-RC1, freezing most chapters
Signed-off-by: John Hauser <31252952+jhauser-us@users.noreply.github.com>

\textbf{%
This chapter is considered stable but could still change before being
ratified as standard by the {\RISCV} International Association.%
}
\bigskip

>>>>

\textbf{%
This chapter is \emph{frozen}, meaning
a functional change is extremely unlikely.
Change will occur only because of some truly critical issue
being identified during public review.%
}
\bigskip

### 2022-11-08 doc/src/preface.tex
Numerous small improvements to the text
Update to 1.0-RC1, freezing most chapters
Signed-off-by: John Hauser <31252952+jhauser-us@users.noreply.github.com>

{
\begin{table}[hbt]
\centering
\begin{tabular}{|l|c|c|}
\hline
Chapter                                                  & ISA? & Status \\
\hline
\hline
1.\ Introduction                                         & ---  & Stable \\
2.\ Control and Status Registers (CSRs) Added to Harts   & Yes  & Stable \\
3.\ Incoming MSI Controller (IMSIC)                      & Yes  & Stable \\
4.\ Advanced Platform-Level Interrupt Controller (APLIC) & No   & Stable \\
5.\ Duo-PLIC                                             & No   & Draft \\
6.\ Interrupts for Machine and Supervisor Levels         & Yes  & Stable \\
7.\ Interrupts for Virtual Machines (VS Level)           & Yes  & Stable \\
8.\ Interprocessor Interrupts (IPIs)                     & No   & Stable \\
9.\ IOMMU Support for MSIs to Virtual Machines           & No   & Draft \\
\hline
\end{tabular}
\end{table}
}

The chapters marked in the table as \emph{Stable} are not expected
to change significantly before being put up for ratification,
but changes of all kinds are still possible nonetheless.
The chapters marked \emph{Draft} are very much
at risk of changing before ratification.
An implementation adhering to the current document might not conform
to an eventual ratified Advanced Interrupt Architecture for {\RISCV}.

>>>>

{
\begin{table}[hbt]
\centering
\begin{tabular}{|l|c|c|}
\hline
Chapter                                                  & ISA? & Status \\
\hline
\hline
1.\ Introduction                                         & ---  & Frozen \\
2.\ Control and Status Registers (CSRs) Added to Harts   & Yes  & Frozen \\
3.\ Incoming MSI Controller (IMSIC)                      & Yes  & Frozen \\
4.\ Advanced Platform-Level Interrupt Controller (APLIC) & No   & Frozen \\
5.\ Duo-PLIC                                             & No   & Draft \\
6.\ Interrupts for Machine and Supervisor Levels         & Yes  & Frozen \\
7.\ Interrupts for Virtual Machines (VS Level)           & Yes  & Frozen \\
8.\ Interprocessor Interrupts (IPIs)                     & No   & Frozen \\
9.\ IOMMU Support for MSIs to Virtual Machines           & No   & Draft \\
\hline
\end{tabular}
\end{table}
}

An implementation adhering to the current document might not conform
to an eventual ratified Advanced Interrupt Architecture for {\RISCV}.
The chapters marked in the table as \emph{Frozen} are not expected
to change significantly before being put up for ratification.
The chapters marked \emph{Draft} are very much
at risk of changing before ratification.
